Recent demography drives changes in linked selection across the maize genome

### 2015-11-13 manuscript.tex
updates

\significancetext{Both selection and demographic change play important roles in shaping diversity across the genome, but clear empirical examples of the interplay of these two forces are lacking.
Here we document the combined effects of demography and linked selection on genome-wide diversity in domesticated maize and its wild ancestor teosinte.  We estimate that maize underwent a bottleneck to  $\approx 5\%$ of the size of the ancestral teosinte population, but that recent expansion has resulted in a maize population perhaps orders of magnitude larger than teosinte.  We show that positive selection on new genic mutations has had relatively little effect on genetic diversity, but that selection against deleterious mutations has dramatically reduced diversity in and immediately around genes in both taxa.  We find that the relative impact of selection depends on the age of the polymorphisms evaluated: while older polymorphisms in maize show more limited effects of linked selection, new mutations instead reflect its larger current size and more efficient selection. Our results demonstrate that a complete understanding of genome-wide patterns of diversity will require careful assessment of both demographic history and the effects of linked selection.  } %JRI

>>>>

\significancetext{
Both selection and demographic change play important roles in
shaping diversity across the genome, but there are few clear empirical examples of the interplay of these two forces. Here we document the combined effects of demography and linked selection on genome-wide diversity in domesticated maize and its wild ancestor teosinte. We estimate that although maize underwent a bottleneck to ≈ 5\% of the size of the ancestral teosinte population, recent expansion has resulted in a maize population much larger than teosinte. Positive selection on new genic mutations has had relatively little effect on genetic diversity, but selection against deleterious mutations has dramatically reduced diversity in and immediately around genes in both taxa. The relative impact of selection depends on the age of the polymorphisms evaluated, revealing that a complete understanding of genome-wide patterns of diversity requires careful assessment of both demographic history and the effects of linked selection.
} %JRI
